Benchmarking on Rigetti architecture

### 2022-09-29 txt/manuscript.tex
Correct schemes in section 2.2.2.

\begin{enumerate}
	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on registers 
	$A$ and $B$.
	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$.
	\item Alice performs the conditional binary measurement on the part 
	$B$ based on the output label $i$. 
	\item  Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and 
	makes a decision based on the received label $j$. If $j=0$, then he decides 
	that the the black box contains $\PP_U$. Otherwise, he decides that the 
	black box contains $\PP_{\Id}$. 
\end{enumerate}

@@

Let us take a closer look at the setup for distinguishing von Neumann 
measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of such a 
scheme is to perform the conditional binary measurement. The first limitation of NISQ devices 
is a lack of possibility of implementing the conditional binary measurement. 
The only possible measurement performed on quantum architectures is the measurement 
on a computational basis. 
Here, we present two possible methods that provide a clever way to cross the obstacle (two schemes of practical realization).

The first way is to use a postselection whereas the second method is to apply a controlled unitary. The methods are described above.

@@

\begin{enumerate}
	\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
	\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
	state  $\ket{\psi_{AB}}$.
	\item Alice measures the part $A$ of the input state  $\ket{\psi_{AB}}$ and receives an output label $i$.
	\item  
	From Holevo--Helstrom theorem, 
	 Bob performs the conditional binary measurement $\PP_{V_j^\dagger}$ on the part 	$B$.
	\item They include these cases for which $i = j$. Otherwise, they reject them.
	\item
	Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
	makes a decision based on received label $j$. If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box. Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box. 
\end{enumerate}

The schematic representation of this setup we can see on Fig.~\ref{fig:postsellection}.

@@

	\begin{enumerate}
			\item Alice and Bob prepare entanglement state $\ket{\psi_{AB}}$.
%		\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
%		\rangle. $
		\item Alice performs one of two quantum channels, $\Phi_{\Id}$ and $\Phi_{U}$,  on part $A$ of the input 
		state  $\ket{\psi_{AB}}$.
		\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from Holevo--Helstrom theorem.	
		\item Alice and Bob prepare the measurement $\Delta$ in computational basis on theirs systems.
		\item Bob	makes a decision based on received label $j$. If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box. Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box.

	\end{enumerate}

\begin{figure}[h!]
	\centering 
	\includegraphics[scale=1.5]{pics/controlled_unitary}

>>>>

\begin{enumerate}
	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on systems 
	$A$ and $B$.
	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$.
	\item Alice performs the conditional binary measurement on the part 
	$B$ based on the output label $i$. 
	\item  Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and 
	makes a decision based on the received label $j$. If $j=0$, then he decides 
	that the the black box contains $\PP_U$. Otherwise, he decides that the 
	black box contains $\PP_{\Id}$. 
\end{enumerate}

@@

Let us take a closer look at the setup for distinguishing von Neumann 
measurements (see Fig.~\ref{fig:theoretical_scheme}). One of the components of 
this scheme is to perform the conditional binary measurement. 
Unfortunately, current NISQ devices do not allow for performing conditional 
binary measurements.
The only possible measurement performed on quantum architectures is the 
measurement in the computational basis. 
We  will present two possible methods providing a clever way to cross this 
obstacle. These will be two schemes of practical realization. 
The first method consists in using post-selection while the second method 
consists in applying a controlled unitary. These methods are described below.

@@

\begin{enumerate}
\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on systems 
$A$ and $B$.
\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or 
$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
\item Alice measures part $A$ of the input state  $\ket{\psi_{AB}}$ and 
receives an output label $i$.
\item  
From Holevo--Helstrom theorem, Bob performs the conditional binary 
measurement	$\PP_{V_j^\dagger}$ on part $B$.
\item They include the cases for which $i = j$.\todo{?} Otherwise, they reject 
them. 
\item Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and makes a
decision based on received label $j$. If $j=0$, then he decides that the the
black box contains $\PP_U$. Otherwise, he decides that the black box contains
$\PP_{\Id}$.
\end{enumerate}

The schematic representation of this setup is depicted in 
Fig.~\ref{fig:postsellection}.

@@

\begin{enumerate}
\item Alice and Bob prepare an entangled state $\ket{\psi_{AB}}$ on 
systems $A$ and $B$..
%\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
%\rangle. $
\item Alice performs one of two quantum channels, either $\Phi_{\Id}$ or
$\Phi_{U}$,  on part $A$ of the input state  $\ket{\psi_{AB}}$.
\item Alice and Bob implement controlled unitary $V_0 \oplus V_1$ obtained from 
Holevo--Helstrom theorem.	
\item Alice and Bob prepare the measurement $\Delta$ in computational basis on 
their systems.
\item Bob makes a decision based on received label $j$. If $j=0$, then he
decides that the the black box contains $\PP_U$. Otherwise, he decides that the
black box contains $\PP_{\Id}$.
\end{enumerate}

The schematic representation of this setup is depicted in 
Fig.~\ref{fig:controlled}.     
\begin{figure}[h!]
	\centering 
	\includegraphics[scale=1.5]{pics/controlled_unitary}
